### 2022-01-09 paper/manuscript.Rmd
minor update

To equalize predictor scales, an often-used technique is standardization ([@gelman2008scaling]). Standardization sets the mean of all predictors to 0 and their standard deviation to 1. It does so by transforming all observations in the predictor space $\boldsymbol{X}$ to Z-scores as follows:

$$
\mathbf{Z} = \frac{\mathbf{X}- \bar{\mathbf{X}}}{\mathbf{s_X}}
$$
where $\mathbf{X}$ is the matrix of predictors, $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors. `brma()` standardizes the predictors by default, on which the model is estimated. The function returns the estimated parameters back in their original scales. This is achieved for the intercept by applying:

>>>>

Thus, to equalize predictor scales, a widely used technique is standardization ([@gelman2008scaling]). Standardization sets the mean of all predictors to 0 and their standard deviation to 1. It does so by transforming all observations in the predictor space $\mathbf{X}$ to Z-scores as follows:

$$
\mathbf{Z} = \frac{\mathbf{X}- \bar{\mathbf{X}}}{\mathbf{s_X}}
$$
where $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors. `brma()` standardizes the predictors by default, on which the model is estimated. The function returns the estimated parameters back in their original scales. This is achieved for the intercept by applying:
